---
title: "Future Predicted Value"
author: "Your Name"
date: "2020-01-01" # fix the date!
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=F)
```

## Future Predicted Value

Future predicted value is the estimate of how much someone will spend in the future with a 
company. In this report we calculate FPV for the Wedge in 2015 using data from before that 
year. Our report has the following sections: 

1. Variable selection: In this section we describe the variables that we use in the model.
1. Model formulation: This section describes the model itself. 
1. Estimates of model accuracy: We run a quick analysis of model accuracy in the final section.

```{r includes}
# Feel free to adjust to the ones you need.
library(tidyverse)
library(scales)
library(reshape2)
library(DBI)
library(broom)

```


```{r db-hookup}
# Change to your path
path.to.db <- paste0("C:/Users/jchan/Dropbox/",
                      "Teaching/AppliedDataAnalytics/",
                      "repos/wedge-solution/")

# Creating the connection to the DB. Similar to 
# a cursor. 
con <- dbConnect(RSQLite::SQLite(),
                 dbname=paste0(path.to.db,"wedge_reporting.db"))

# Listing the tables
#dbListTables(con) # uncomment to see table names

# And creating connections to the two tables. 
owner.ym <- tbl(con, "owner_year_month")

```

### Variable Selection

```{r variable-selection}
# Use this space to create the data set you'll feed into `lm` I've made a simple one for you.
# I've done this in two different ways so you can see a couple of techniques.

# First way uses "pivot_wider"
md <- owner.ym %>% 
  filter(card_no != "3",
         between(year,2013,2015)) %>% 
  group_by(card_no,year) %>%
  summarize(sales=sum(sales,na.rm=T)) %>% 
  ungroup() %>% 
  collect 

md <- md %>% 
  pivot_wider(id_cols=c("card_no"),
              names_from=year,
              names_prefix="sales_",
              values_from=sales)

# Second builds a data set up from the ground
md2 <- owner.ym %>% 
  filter(card_no != "3",
         between(year,2013,2015)) %>% 
  distinct(card_no) %>% 
  collect 

# Now start bringing in our covariates. 
md2 <- left_join(md2,
                owner.ym %>% 
                  filter(year==2013) %>% 
                  group_by(card_no) %>% 
                  summarize(sales_2013 = sum(sales)) %>% 
                  collect,
                by="card_no") 

md2 <- left_join(md2,
                owner.ym %>% 
                  filter(year==2014) %>% 
                  group_by(card_no) %>% 
                  summarize(sales_2014 = sum(sales)) %>% 
                  collect,
                by="card_no") 

md2 <- left_join(md2,
                owner.ym %>% 
                  filter(year==2015) %>% 
                  group_by(card_no) %>% 
                  summarize(sales_2015 = sum(sales)) %>% 
                  collect,
                by="card_no") 


```

<!-- 

After you build your data set, explain what the variables you created are.
 
--> 

### Model Formulation

```{r modeling}
# A simple example model

lm.1 <- lm(sales_2015 ~ sales_2013 + sales_2014,
           data=md,
           subset=sales_2014 <= 10000)

# Of course, you'd never just dump a summary table into a document!
print(tidy(lm.1))
```

<!--

Do a short write up of your model. What terms are significant? What's the R^2? What's the 
residual standard error and how would you interpret it?
-->

### Model Accuracy

```{r model-accuracy}

# your code here

```

<!--

As the readme indicates, do a quick check of model accuracy on a holdout sample that
isn't use for fitting.

-->

